### 2022-04-08 manuscript.tex
pics [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/afca29ccc7e85bd9ed22a802be561104666cc46a.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/afca29ccc7e85bd9ed22a802be561104666cc46a/checks
https://github.com/scherzerthesis/thesis/actions/runs/2116432672

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/8fec467e841dcc3635a7c267f4d9f98ccfd8224c/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/8fec467e841dcc3635a7c267f4d9f98ccfd8224c}{scherzerthesis/thesis@8fec467}
on April 8, 2022.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/afca29ccc7e85bd9ed22a802be561104666cc46a/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/afca29ccc7e85bd9ed22a802be561104666cc46a}{scherzerthesis/thesis@afca29c}
on April 8, 2022.
